\begin{thebibliography}{9}
\bibitem{huber1}
Huber, Nikolaus, et al. \emph{Analysis of the performance-influencing factors of virtualization platforms.}  On the Move to Meaningful Internet Systems, OTM 2010. Springer Berlin Heidelberg, 2010. 811-828.
\bibitem{huber2}
Huber, Nikolaus, et al. \emph{A Method for Experimental Analysis and Modeling of Virtualization Performance Overhead.}  Cloud Computing and Services Science. Springer New York, 2012. 353-370.
\bibitem{tickoo} 
Tickoo, Omesh, et al.  \emph{Modeling virtual machine performance: challenges and approaches.}  ACM SIGMETRICS Performance Evaluation Review 37.3 (2010): 55-60.
\bibitem{menon} Menon, Aravind, et al.  \emph{Diagnosing performance overheads in the xen virtual machine environment.}  Proceedings of the 1st ACM/USENIX international conference on Virtual execution environments. ACM, 2005.
\bibitem{kundu}Kundu, Sajib, et al.  \emph{Application performance modeling in a virtualized environment.}  High Performance Computer Architecture (HPCA), 2010 IEEE 16th International Symposium on. IEEE, 2010.
\bibitem{cherkasova}
Cherkasova, Ludmila, and Rob Gardner.  \emph{Measuring CPU overhead for I/O processing in the Xen virtual machine monitor.}  Proceedings of the USENIX annual technical conference. 2005.
\bibitem{traeger}
Traeger, Avishay, Ivan Deras, and Erez Zadok.  \emph{DARC: Dynamic analysis of root causes of latency distributions.}  ACM SIGMETRICS Performance Evaluation Review 36.1 (2008): 277-288
\bibitem{knapp1}
Knapp, Rashawn L., Karen L. Karavanic, and Douglas M. Pase.  \emph{Detecting runtime environment interference with parallel application behavior.}  Parallel and Distributed Processing Symposium, 2007. IPDPS 2007. IEEE International. IEEE, 2007.
\bibitem{kprobes}
Kprobes   https://www.kernel.org/doc/Documentation/kprobes.txt
\bibitem{paul}
Paul, Indrani, Sudhakar Yalamanchili, and Lizy K. John.  \emph{Performance impact of virtual machine placement in a datacenter.}  Performance Computing and Communications Conference (IPCCC), 2012 IEEE 31st International. IEEE, 2012.
\bibitem{mucci}
Mucci, Philip J., et al.  \emph{PAPI: A portable interface to hardware performance counters.}  Proc. Department of Defense HPCMP Users Group Conference. 1999.
\bibitem{mohror}
Mohror, Kathryn, and Karen L. Karavanic.  \emph{Towards scalable event tracing for high end systems.}  High Performance Computing and Communications. Springer Berlin Heidelberg, 2007. 695-706.
\bibitem{kufrin}
Kufrin, Rick.  \emph{Perfsuite: An accessible, open source performance analysis environment for linux.}  6th International Conference on Linux Clusters: The HPC Revolution. Vol. 151. 2005.
\bibitem{jafar}
Jafar, Anderson, and Abdullat (2008). \emph{Comparison of Dynamic Web Content Processing Language Performance Under a LAMP Architecture}  Journal of Information Systems Applied Research, 1 (1). \url{http://jisar.org/1/1/. ISSN: 1946-1836.}
\bibitem{saltzer}
Saltzer, Jerome H., David P. Reed, and David D. Clark.  \emph{End-to-end arguments in system design.}  ACM Transactions on Computer Systems (TOCS) 2.4 (1984): 277-288.
\bibitem{katcher}
Katcher, Jeffrey. Postmark: A new file system benchmark. Technical Report TR3022, Network Appliance, 1997. www. netapp. com/tech\_library/3022. html, 1997.
\bibitem{gupta1}
Gupta, Vishakha, Rob Knauerhase, and Karsten Schwan.  \emph{Attaining system performance points: revisiting the end-to-end argument in system design for heterogeneous many-core systems.}  ACM SIGOPS Operating Systems Review 45.1 (2011): 3-10.
\bibitem{levon}
Levon, John, and Philippe Elie.  \emph{Oprofile: A system profiler for linux.}  2012-05-05. \url{http://oprofile, sf. net (2004).}
\bibitem{tikotekar}
Tikotekar, Anand, et al.  \emph{An analysis of hpc benchmarks in virtual machine environments.}  Euro-Par 2008 Workshops-Parallel Processing. Springer Berlin Heidelberg, 2009.
\bibitem{santos}
Santos, Renato J.  “Tutorial:  Profiling in Xen” \url{http://xen.xensource.com/files/summit\_3/xenoprof\_tutorial.pdf}  HP Labs  Xen Summit, 2006
\bibitem{menon2}
Menon, Santos, Yoshio, Janakiraman.  XENOPROF – Performance profiling in Xen.  User Guide.   \url{http://xenoprof.sourceforge.net/xenoprof\_2.0.txt}  2005.
\bibitem{joukov}
Joukov, Nikolai, et al.  \emph{Operating system profiling via latency analysis.}  Proceedings of the 7th symposium on Operating systems design and implementation. USENIX Association, 2006.
\bibitem{gupta2}
Gupta, Vishakha, et al.  \emph{Pegasus: Coordinated scheduling for virtualized accelerator-based systems.}  2011 USENIX Annual Technical Conference (USENIX ATC’11). 2011.
\bibitem{ahmad}
Ahmad, Irfan, Ajay Gulati, and Ali Mashtizadeh.  \emph{vIC: Interrupt coalescing for virtual machine storage device IO.}  USENIX Annual Technical Conference (ATC). 2011.
\bibitem{amit}
Amit, Nadav, et al.  \emph{vIOMMU: efficient IOMMU emulation.}  USENIX Annual Technical Conference (ATC). 2011.
\bibitem{lim}
Lim, Harold, Aman Kansal, and Jie Liu.  \emph{Power budgeting for virtualized data centers.}  2011 USENIX Annual Technical Conference (USENIX ATC’11). 2011.
\bibitem{vmwareMem}
VMware, Inc.  Performance Study.  \emph{Understanding Memory Resource Management in VMware ESX 4.1.} \url{http://www.vmware.com/files/pdf/techpaper/vsp\_41\_perf\_memory\_mgmt.pdf}
\bibitem{boutcher}
Boutcher, David, and Chandra Abhishek. \emph{Does Virtualization Make Disk Scheduling Passé?}  Univerisity of Minnesota.  \url{http://www-users.cs.umn.edu/~chandra/papers/hotstorage09/paper.pdf}
\bibitem{diskeeper}
Diskeeper, Inc.  \emph{Virtualization and Disk Performance}  \url{http://files.diskeeper.com/pdf/virtualization\_performance.pdf}
\bibitem{IBMsar}
IBM, Inc. \emph{Assessing disk performance with the sar command}  \url{http://publib.boulder.ibm.com/infocenter/pseries/v5r3/index.jsp?topic=/com.ibm.aix.prftungd/doc/prftungd/assess\_disk\_perf\_sar.htm}
\bibitem{soundararajan}
Soundararajan, Gokul, and Cristiana Amza.  \emph{Towards end-to-end quality of service: controlling I/O interference in shared storage servers.}  Proceedings of the 9th ACM/IFIP/USENIX International Conference on Middleware. Springer-Verlag New York, Inc., 2008.
\bibitem{lumb}
Lumb, Christopher R., Arif Merchant, and Guillermo A. Alvarez.  \emph{Façade: Virtual storage devices with performance guarantees.}  (2003).
\bibitem{knapp2}
Knapp, Rashawn L., R. L. Pase, and Karen L. Karavanic.  \emph{ARUM: application resource usage monitor.}  9th Linux Clusters Institute International Conference on High-Performance Clustered Computing. 2008.
\bibitem{gartners}
Bittman, Thomas J.  \emph{Cloud Computing:  Defining and Describing an Emerging Phenomenon.}  Gartner Research, March (2008).
\bibitem{nist}
Mell, Peter, and Timothy Grance. "The NIST Definition of Cloud Computing." NIST special publication 800-145 (2011).
\bibitem{ramya}
Catherine, M. Ramya, and E. Bijolin Edwin.  \emph{A Survey on Recent Trends in Cloud Computing and its Application for Multimedia.}  International Journal of Advanced Research in Computer Engineering \& Technology (IJARCET) 2.1 (2013): pp-304.
\bibitem{vmWareIO} 
VMware, Inc. \emph{Storage system performance analysis with IOmeter.}  \url{http://communities.vmware.com/docs/DOC-3961}
\bibitem{suseIO} 
Suse Chapter 13.  \emph{Tuning I/O Performance.}  \url{http://doc.opensuse.org/products/draft/SLES/SLES-tuningsdraft/cha.tuning.io.html}
\bibitem{hplBench} 
\emph{HPL Benchmark: the Linpack TPP benchmark which measures the floating point rate of execution for solving a linear system of equations.}  \url{http://www.netlib.org/benchmark/hpl/}
\bibitem{hpcChallenge} 
\emph{HPC Challenge:}  \url{http://icl.cs.utk.edu/hpcc/}
\bibitem{pgTune} 
Momjian, Bruce. \emph{PostgresSQL Hardware Performance Tuning.}  \url{http://momjian.us/main/writings/pgsql/hw\_performance/}
\bibitem{du1} 
Du, Jiaqing, Nipun Sehrawat, and Willy Zwaenepoel.  \emph{Performance profiling in a virtualized environment.}  Proc. HotCloud (2010).
\bibitem{du2}
Du, Jiaqing, Nipun Sehrawat, and Willy Zwaenepoel.  \emph{Performance profiling of virtual machines.}  ACM SIGPLAN Notices. Vol. 46. No. 7. ACM, 2011.
\bibitem{serebrin}
Serebrin, Benjamin, and Daniel Hecht.  \emph{Virtualizing performance counters.}  Euro-Par 2011: Parallel Processing Workshops. Springer Berlin Heidelberg, 2012.
\bibitem{buell1}
Buell, J., Hecht, D., Heo, J., Saladi, K. and Taheri, H. R.  \emph{Methodology for Performance Analysis of VMware vSphere under Tier-1 Applications.}  VMware Technical Journal Vol 2. No. 1.  June 2013.
\bibitem{buell2} 
Buell, J., Hecht, D., Heo, J., Saladi, K. and Taheri, H. R.  \emph{Overcommitment in the ESX Server.}  VMware Technical Journal Vol 2. No. 1.  June 2013.
\bibitem{ioping} 
\emph{ioping.}  Simple disk I/O latency measuring tool.  \url{https://code.google.com/p/ioping/}
\bibitem{iostats} I/O statistics fields. \url{https://www.kernel.org/doc/Documentation/iostats.txt}
\bibitem{proc} THE /proc FILESYSTEM. \url{https://www.kernel.org/doc/Documentation/filesystems/proc.txt}
\bibitem{diskstats} I/O statistics of block devices. \url{https://www.kernel.org/doc/Documentation/ABI/testing/procfs-diskstats}
\bibitem{memory} Memory Resource Controller. \url{https://www.kernel.org/doc/Documentation/cgroups/memory.txt}
\bibitem{winperf} Windows Performance Toolkit. \url{http://msdn.microsoft.com/en-us/library/windows/hardware/hh162945.aspx}
\bibitem{wood} Wood, Timothy, et al. "Disaster recovery as a cloud service: Economic benefits and deployment challenges." 2nd USENIX Workshop on Hot Topics in Cloud Computing. 2010.
\bibitem{tsafrir} Tsafrir, Dan, et al. \emph{System noise, OS clock ticks, and fine-grained parallel applications.} Proceedings of the 19th annual international conference on Supercomputing. ACM, 2005.
\bibitem{netflix} Link, David.  \emph{Netflix and Stolen Time} \url{http://blog.sciencelogic.com/netflix-steals-time-in-the-cloud-and-from-users/03/2011} 
\bibitem{xenbus} \emph{XenBus} \url{http://wiki.xen.org/wiki/XenBus}
\bibitem{vmwarepubs} \emph{Vshpere Guest Programming Guide} \url{https://www.vmware.com/support/developer/guest-sdk/guest\_sdk\_40.pdf}
\bibitem{citrix} \emph{Citrix XenServer 6.1.0 Storage Performance Guide}.  Citrix, Inc. 2013.
\end{thebibliography}

